FictionEro2 - Affective Impact of Fiction

### 2025-02-28 study2/analysis/2_emotion.qmd
added dapipe to save only demo_data

**notes**: How about confidence on all AI and all photos

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, SexualActivity,
           -Feedback_Text),
    by = "Participant"
    ) |> 
  mutate(Condition = fct_relevel(Condition, "Reality", "Fiction"),
         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         GenderualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Reality" & Realness > 0.5 ~ "True",
           Condition == "AI-Fiction" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |> 
  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))

@@

@@

@@

```{r}
valence <- df |> 
  ggplot(aes(x=Valence)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasa")) +
  labs(title = "Valence") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        legend.position = "none")

@@

@@

>>>>

**notes**: How about confidence on all AI and all photos.

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, GenderualActivity,
           -Feedback_Text),
    by = "Participant"
    ) |> 
  mutate(Condition = fct_relevel(Condition, "Reality", "Fiction"),
         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         GenderualActivity_num = as.numeric(as.factor(GenderualActivity)),
         ConditionBelief = case_when(
           Condition == "Reality" & Realness > 0.5 ~ "True",
           Condition == "AI-Fiction" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |> 
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))

@@

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Arousal, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Enticing, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

```{r}
valence <- df |> 
  ggplot(aes(x=Valence)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasant")) +
  labs(title = "Valence") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        legend.position = "none")

@@

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Valence, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

:::

## Arousal

```{r}
#| fig-height: 12
#| fig-width: 7

plot_descriptive <- function(df, target="Arousal") {
  # By item
  order <- df |>
    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
    summarize(mean = mean(.data[[target]], na.rm=TRUE), .by=c("Condition", ".Item_Order")) |> 
    arrange(.Item_Order, desc(Condition)) |> 
    mutate(diff = sign(mean - lag(mean)),
           Relevance = str_extract(.Item_Order, "^[^_]+"),
           .Item_Order = str_extract(.Item_Order, "(?<=_).+")) |>
    filter(Condition == "Photograph") |> 
    arrange(Relevance, diff, mean)

  p1 <- df |>
    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
    group_by(.Item_Order, Condition) |>
    ggdist::mean_qi(.data[[target]], .width=0.95) |>
    mutate(Gender = fct_rev(str_extract(.Item_Order, "^[^_]+"))) |>
    left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
    # mutate(.average = mean(.data[[target]]), .by="Item") |>
    # mutate(Item = fct_reorder(Item, .average)) |>
    ggplot(aes(y = .Item_Order, x=.data[[target]])) +
    geom_line(aes(color=as.factor(diff)), linewidth=1) +
    geom_point(aes(color=Condition), size=2) +

    # ggdist::stat_slabinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    # ggdist::stat_histinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336", "1"="#F44336", "-1"="#2196F3"),
                       breaks = c('AI-Generated', 'Photograph')) +
    # scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
    scale_y_discrete(labels = function(x) str_extract(x, "(?<=_).+")) +
    theme_minimal() +
    theme(panel.grid.minor.x = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank()) +
    labs(title = paste0(target, " by Item"), color="Condition", y="Items") +
    facet_wrap(~Gender, scales="free_y")

  # By participant
  p2 <- df |>
    summarize(.average = mean(.data[[target]]),
              .by=c("Gender", "Participant", "Condition")) |>
    pivot_wider(names_from = Condition, values_from = .average) |>
    mutate(.diff = Photograph - `AI-Generated`) |>
    mutate(Participant = fct_reorder(Participant, .diff)) |>
    ggplot(aes(x = .diff, y=Participant)) +
    geom_bar(aes(fill=.diff), stat = "identity")  +
    scale_fill_gradient2(guide="none", low="red", high="red", mid="blue") +
    labs(title = paste0(target, " by Participant")) +
    facet_wrap(~Gender, ncol=2, scales="free_y") +
    theme_minimal() +
    theme(panel.grid.major.y = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.text.y = element_blank()) +
    labs(title = paste0(target, " by Participant"), x="Difference (Photograph - AI-Generated)", y="Participants")

  p1 / p2 + plot_layout(heights = c(2, 1))
}

# remove other 
arousal_desc <- df |> 
  filter(Gender != "Other") |> 
  plot_descriptive("Arousal")

arousal_desc
```

### Whole Sample

```{r}
